---
title: "eventbriteDataViz"
author: "kimp"
date: "10/18/2018"
output: html_document
---

# Load Libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggthemes)
```

Clean / Review Collected Data
```{r}
# df = result after rbind-ing all the data from 10/3 - 10/17
df <- read.csv("eventbrite.csv")

# check unique events vs total events
nrow(df) # 1238 total rows
length(unique(df$events.id)) # 133 unique events

# df2 = unique events
df2 <- df[,-(1:3)] %>% unique()
```

Explore relationship between price and events by location.
Note: Data only returns most events from nyc and a handful from LA. Not worth putting on a map, but we can make a bar graph visual.

```{r}
(p <- ggplot(data=df2, aes(x=events.is_free, group=events.start.timezone)) + 
   geom_bar(position="stack", aes(fill=events.start.timezone)) + theme_tufte() + 
   ggtitle("Count of Free and Paid Events") + 
   scale_x_discrete(name = "Event Price", labels = c("FALSE" = "Paid", "TRUE" = "Free")) +
   scale_fill_manual(values=c("#fcfc08", "#20acf7"), name="City",
                         labels=c("Los Angeles", "New York City")) +
   geom_text(stat='count', aes(label = ..count..), position = position_stack(vjust = 0.5), size=10)
)
```

# Extra: dodge graph
```{r}
(p <- ggplot(data=df2, aes(x=events.is_free, group=events.start.timezone)) + 
   geom_bar(position="dodge", aes(fill=events.start.timezone)) + theme_tufte() + 
   ggtitle("Count of Free and Paid Events") + 
   scale_x_discrete(name = "Event Price", labels = c("FALSE" = "Paid", "TRUE" = "Free")) +
   scale_fill_manual(values=c("#fcfc08", "#86edf7"), name="City",
                         labels=c("Los Angeles", "New York City")) +
   geom_text(stat='count', aes(label = ..count..), position = position_dodge(0.9), vjust = 0)
)
```

Explore relationship between price and events.

```{r}
df2 <- filter(df2, events.start.timezone=="America/New_York") # filter only NY events
nrow(df2) # 166 unique rows... some events share same ID but have multiple occurences

(p <- ggplot(data=df2, aes(x=events.is_free, fill=events.is_free)) + 
   geom_bar() + theme_tufte() + 
   ggtitle("Count of Free and Paid Events") + 
   scale_x_discrete(name = "Event Price", labels = c("FALSE" = "Paid", "TRUE" = "Free")) +
   scale_fill_discrete(name="Event Price",
                         labels=c("Paid", "Free")) +
   geom_text(color="white",stat='count', aes(label=..count..),vjust=2, size=10)
)
```

Explore frequency of events over time

```{r}
# create df for dates
dfDate <- select(df2, events.start.utc, events.start.timezone, events.is_free, events.name.text)
dfDate$events.start.utc <- as.Date(dfDate$events.start.utc)
str(dfDate)
dfDate2 <- dfDate %>% group_by(events.start.utc, events.is_free) %>% count() %>% ungroup() # count events by date

# bar plot
(p <- ggplot(dfDate2, aes(x=events.start.utc, y=n, fill=events.is_free)) +
   geom_bar(stat="identity") + xlab("") + theme_tufte() +
   ggtitle("Count of Free and Paid Events") +
   scale_fill_discrete(name="Event Price", labels=c("Paid", "Free")) +
   scale_x_date(date_breaks = "months" , date_labels = "%b-%y", limits = as.Date(c("2018-09-1", "2018-12-31"))) +
   facet_grid(events.is_free~.) +
   theme(strip.text.y = element_blank())
)

# plot october counts
(p <- ggplot(dfDate2, aes(x=events.start.utc, y=n, fill=events.is_free)) +
   geom_bar(stat="identity") + xlab("") + theme_tufte() +
   ggtitle("Count of Free and Paid Events (October)") +
   scale_fill_discrete(name="Event Price", labels=c("Paid", "Free")) +
   scale_x_date(date_breaks = "day" , date_labels = "%m-%d-%y", limits = as.Date(c("2018-10-1", "2018-10-28"))) +
   facet_grid(events.is_free~.) +
   theme(strip.text.y = element_blank()) +
   theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
   geom_text(aes(label=n), hjust = "center", vjust = 1)
)

# plot november counts
(p <- ggplot(dfDate2, aes(x=events.start.utc, y=n, fill=events.is_free)) +
   geom_bar(stat="identity") + xlab("") + theme_tufte() +
   ggtitle("Count of Free and Paid Events (November)") +
   scale_fill_discrete(name="Event Price", labels=c("Paid", "Free")) +
   scale_x_date(date_breaks = "day" , date_labels = "%m-%d-%y", limits = as.Date(c("2018-11-2", "2018-11-27"))) +
   facet_grid(events.is_free~.) +
   theme(strip.text.y = element_blank()) +
   theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
   geom_text(aes(label=n), hjust = "center", vjust = 1)
)

# plot december counts
(p <- ggplot(dfDate2, aes(x=events.start.utc, y=n, fill=events.is_free)) +
   geom_bar(stat="identity") + xlab("") + theme_tufte() +
   ggtitle("Count of Free and Paid Events (December)") +
   scale_fill_discrete(name="Event Price", labels=c("Paid", "Free")) +
   scale_x_date(date_breaks = "day" , date_labels = "%m-%d-%y", limits = as.Date(c("2018-12-1", "2018-12-28"))) +
   facet_grid(events.is_free~.) +
   theme(strip.text.y = element_blank()) +
   theme(axis.text.x = element_text(angle = 70, hjust = 1)) +
   geom_text(aes(label=n), hjust = "center", vjust = 1)
)
```

Text Analysis of Event Names

```{r}
library(tm)
dyn.load(paste0(system2('/usr/libexec/java_home', stdout = TRUE), '/lib/server/libjvm.dylib'))
library(qdap)
library(qdapRegex)

# Define clean_corpus function
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, content_transformer(replace_symbol))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en")))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, stripWhitespace)
  #corpus <- tm_map(corpus, PlainTextDocument)
  return(corpus)
}


# stem completion function
stemCompletion2 <- function(x, dictionary) {
   x <- unlist(strsplit(as.character(x), " "))
    # # Oddly, stemCompletion completes an empty string to
	  # a word in dictionary. Remove empty string to avoid issue.
   x <- x[x != ""]
   x <- stemCompletion(x, dictionary=dictionary)
   x <- paste(x, sep="", collapse=" ")
   PlainTextDocument(stripWhitespace(x))
}

# df data into completed corpus
df3 <- df2 %>% select(events.id, events.name.text, events.is_free) %>% unique()
df3 <- rename(df3, doc_id=events.id, text=events.name.text)
corp <- VCorpus(DataframeSource(df3)) # df to source to corpus
clea <- clean_corpus(corp) # clean corpus

# Review
corp[[2]][1]
clea[[2]][1]
# s[[2]][1]
#comp[[2]][1]
```

```{r}
# Add meta data to corpus from df
tdm <- TermDocumentMatrix(clea) # convert to term-document-matrix

library(tidytext)
clea.td <- tidy(tdm)

meta <- select(df3, doc_id, events.is_free) # meta data 
colnames(meta) <- c("document", "events.is_free")
meta$document <- as.character(meta$document)
clea.td <- as.data.frame(left_join(clea.td, meta, by="document")) # combine data with meta data

clea.td %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms - Event Names") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

# top 25 words, all
clea.td$events.is_free <- ifelse(clea.td$events.is_free==TRUE, 1, 0)
clea.td_free <- clea.td %>% filter(events.is_free==1)
clea.td_paid <- clea.td %>% filter(events.is_free==0)

# top 25 words, free events
clea.td_free %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms for Free Events Names") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

# top 25 words, paid events
clea.td_paid %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms for Paid Events Names") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

# Pyramid Plot
topwords <- clea.td %>% group_by(events.is_free, term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 30, wt = n)  %>%
                ungroup() %>% 
                arrange(desc(n))
topwords.high <- filter(topwords, events.is_free=="1")
topwords.low <- filter(topwords, events.is_free=="0")
common.words <- left_join(topwords.high, topwords.low, by="term") %>% mutate(difference=abs(n.x-n.y)) %>% arrange(desc(difference)) %>% filter(difference != 'NA')
library(plotrix)
pyramid.plot(common.words$n.x, common.words$n.y, 
                  labels = common.words$term, 
             gap = 20, 
             top.labels = c("Paid Events", " ", "Free Events"), 
             main = "Top Words in Common - Names",
             laxlab = NULL, 
             raxlab = NULL, 
             unit = NULL, 
             labelcex=0.5, show.values=TRUE)
```


Text Analysis of Event Descriptions

```{r}
library(tm)
dyn.load(paste0(system2('/usr/libexec/java_home', stdout = TRUE), '/lib/server/libjvm.dylib'))
library(qdap)
library(qdapRegex)

# Define clean_corpus function
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, removePunctuation)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, content_transformer(replace_symbol))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en")))
  corpus <- tm_map(corpus, removeNumbers)
  corpus <- tm_map(corpus, stripWhitespace)
  #corpus <- tm_map(corpus, PlainTextDocument)
  return(corpus)
}


# Dr. Brambor's stem completion function
stemCompletion2 <- function(x, dictionary) {
   x <- unlist(strsplit(as.character(x), " "))
    # # Oddly, stemCompletion completes an empty string to
	  # a word in dictionary. Remove empty string to avoid issue.
   x <- x[x != ""]
   x <- stemCompletion(x, dictionary=dictionary)
   x <- paste(x, sep="", collapse=" ")
   PlainTextDocument(stripWhitespace(x))
}

# df data into completed corpus
df3 <- df2 %>% select(events.id, events.description.text, events.is_free) %>% unique()
df3 <- rename(df3, doc_id=events.id, text=events.description.text)
corp <- VCorpus(DataframeSource(df3)) # df to source to corpus
clea <- clean_corpus(corp) # clean corpus


# Review
corp[[2]][1]
clea[[2]][1]
# s[[2]][1]
#comp[[2]][1]

# Add meta data to corpus from df
tdm <- TermDocumentMatrix(clea) # convert to term-document-matrix

library(tidytext)
clea.td <- tidy(tdm)

meta <- select(df3, doc_id, events.is_free) # meta data 
colnames(meta) <- c("document", "events.is_free")
meta$document <- as.character(meta$document)
clea.td <- as.data.frame(left_join(clea.td, meta, by="document")) # combine data with meta data

# top 25 words, all
clea.td %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms - Event Descriptions") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

clea.td$events.is_free <- ifelse(clea.td$events.is_free==TRUE, 1, 0)
clea.td_free <- clea.td %>% filter(events.is_free==1)
clea.td_paid <- clea.td %>% filter(events.is_free==0)

# top 25 words, free events
clea.td_free %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms for Free Events Descriptions") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

# top 25 words, paid events
clea.td_paid %>%  group_by(term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 25, wt = n)  %>%
                ungroup() %>%
                mutate(term = reorder(term, n)) %>%
ggplot(aes(x = term, y = n, fill = n)) + 
  geom_bar(stat = "identity") + 
  geom_text(aes(label=n, x=term, y=n-1), hjust = 1, color="white") +
  xlab(NULL) +  coord_flip() + theme_fivethirtyeight() +
  ggtitle("Top 25 Frequent Terms for Paid Events Descriptions") + 
  scale_colour_gradientn(colours=rainbow(4)) +
  theme(legend.position="none")

# Pyramid Plot
topwords <- clea.td %>% group_by(events.is_free, term) %>%
                summarise(n = sum(count)) %>%
                top_n(n = 30, wt = n)  %>%
                ungroup() %>% 
                arrange(desc(n))
topwords.high <- filter(topwords, events.is_free=="1")
topwords.low <- filter(topwords, events.is_free=="0")
common.words <- left_join(topwords.high, topwords.low, by="term") %>% mutate(difference=abs(n.x-n.y)) %>% arrange(desc(difference)) %>% filter(difference != 'NA')
library(plotrix)
pyramid.plot(common.words$n.x, common.words$n.y, 
                  labels = common.words$term, 
             gap = 1500, 
             top.labels = c("Paid Events", " ", "Free Events"), 
             main = "Top Words in Common - Names",
             laxlab = NULL, 
             raxlab = NULL, 
             unit = NULL, 
             labelcex=0.5, show.values=TRUE)
```

